Staged Abstract Interpreters

### 2019-02-13 paper/10_intro.tex
code & revision

\begin{lstlisting}
def power5(b: Int) = b * b * b * b * b
\end{lstlisting}

@@

%artifacts of concrete semantics can be refactored to abstract interpreters.
In this paper, we study the confluence of two old ideas --- Futamura projection and
abstract interpretation, but from the perspective of their recent realizations
--- multi-stage programming and definitional abstract interpreters.
To be specific, we present the application of the first Futamura projection on
definitional abstract interpreters, which intersects as staged abstract interpreters.
By borrowing the ideas from \note{monadic interpreters} and embedded
domain-specific languages, we develop an approach to fulfill four different
semantics (Figure~\ref{confluence}) in a unified framework. \todo{explain four sem}

>>>>

\begin{lstlisting}
def power5(b: Int) = b * b * b * b * b * 1
\end{lstlisting}

@@

In this paper, we study the confluence of two old ideas --- Futamura projection
and abstract interpretation, but from the perspective of their recent
realizations --- multi-stage programming and definitional abstract interpreters.
To be specific, we present the application of the first Futamura projection on
definitional abstract interpreters, which intersects as staged abstract
interpreters. By borrowing the ideas from \note{monadic interpreters}
\cite{DBLP:conf/popl/LiangHJ95, DBLP:journals/pacmpl/DaraisLNH17,
Sergey:2013:MAI:2491956.2491979} and embedded domain-specific languages
\cite{DBLP:conf/snapl/RompfBLSJAOSKDK15, DBLP:journals/jfp/CaretteKS09,
DBLP:conf/icfp/GibbonsW14}, we develop an approach to fulfill four different
semantics (Figure~\ref{confluence}) in a unified framework. The four semantics
share one same generic interpreter and some abstract types; by instantiating the
abstract types differently, the interpreter behaves as a concrete interpreter,
an abstracter interperter, or their staged versions, respectively.
